Manuscript figures

### 2024-02-05 04_manuscript_plots.Rmd
moving panels and other edits

lake_sites <- c('TOOK', 'PRLA','PRPO', 'CRAM', 'LIRO','BARC', 'SUGG')
cols_modeltype <- c('empirical' = "#482576FF",
                    'multi-model ensemble' =  "#35608DFF",
                    'process' = "#21908CFF",
                    'ML' = '#BBDF27FF',
                    'null' = '#A9A9A9')
# read in the metadata from the google sheet
googlesheets4::gs4_deauth()
model_meta <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1oC7_w63wSCXNiHs1IK8AFGr0MG-NdjDAjwkfjvRZW-I/edit?usp=sharing")

@@

```{r model-type, fig.width=10}
top10_temp <- 
  temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |>
  slice_max(mean_crps, n= 10, na_rm = T) |>
  left_join(model_meta) |> 
  mutate(model_id = fct_reorder(model_id, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no')) |> 
  ggplot(aes(x=mean_crps, y = model_id, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_NOAA)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", 
                   pattern_spacing = 0.04,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model', x = 'mean CRPS skill (vs climatology)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw() + 
  guides(pattern = guide_legend(override.aes = list(fill = "white", pattern_spacing = 0.02), 
                                title = 'Uses weather covariates?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model type'))

all_temp <- 
  temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(model_meta) |> 
  mutate(model_id = fct_reorder(model_id, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no')) |> 
  ggplot(aes(x=mean_crps, y = model_id, fill = model_type)) +    # Different pattern for each group

  geom_bar_pattern(aes(pattern = as.factor(uses_NOAA)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", width = 0.8,
                   pattern_spacing = 0.03,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model', x = 'mean CRPS skill (vs climatology)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe'), name = 'Uses weather covariates?') +
  scale_pattern_type_manual(values=c(NA, NA), name = 'Uses weather covariates?') +
  theme_bw() + 
  guides(pattern = guide_legend(override.aes = list(fill = "white"), title = 'Uses weather covariates?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model type'))

@@

## Figure 2
```{r horizon-score}
# top 10 average models
top_mods <- temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |> 
  slice_max(mean_crps, n = 10, na_rm = T) |> 
  distinct(model_id)

B <- 
  temperature_skill |> 
  filter(model_id %in% top_mods$model_id) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = fct_reorder(model_id, mean_crps, .desc = T))) +
  geom_hline(yintercept = 0) + 
  geom_line()  +  
  labs(y='mean CRPS skill (vs climatology)', x = 'Horizon (days)') +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw()

ggpubr::ggarrange(B) |> 
  ggsave(filename = 'Plots/Figure2.png', width = 15, height = 17, units = 'cm')
```

## Figure 3
```{r bias-sd}
# top 10 average models
top_mods <- temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |> 
  slice_max(mean_crps, n = 10, na_rm = T) |> 
  mutate(model_id = fct_reorder(model_id, mean_crps, .desc = T)) |> 
  distinct(model_id)

sd <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime)) |> 
  filter(model_id %in% top_mods$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_sd = mean(sd, na.rm = T)) |> 
  mutate(model_id = factor(model_id, levels = levels(top_mods$model_id))) |> 
  ggplot(aes(x=horizon, 
             y = mean_sd, colour = model_id)) +
  geom_line()+
  labs(y='mean standard deviation', x = 'Horizon (days)') +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw()

bias <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime),
         abs_bias = abs(mean - observation)) |> 
  filter(model_id %in% top_mods$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_abs_bias = mean(abs_bias, na.rm = T)) |> 
  mutate(model_id = factor(model_id, levels = levels(top_mods$model_id))) |> 
  ggplot(aes(x=horizon, 
             y = mean_abs_bias, colour = model_id)) +
  geom_line()+
  labs(y='mean absolute bias', x = 'Horizon (days)') +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw() +
  coord_cartesian(ylim = c(0, 2.5))

ggpubr::ggarrange(sd, bias, labels = 'auto', align = 'v', nrow = 2, common.legend = T, legend = 'right') |> 
  ggsave(filename = 'Plots/Figure3.png', height = 15, width = 14, units = 'cm')
```

## Figure 4

@@

good_80 <- 
  plot_reliability(scores = temperature_scores,
                            models = top_mods$model_id, 
                            CI = 80, 
                            order = levels(top_mods$model_id)) +
  scale_color_brewer(name = 'Top Models', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

good_95 <- plot_reliability(scores = temperature_scores,
                            models = top_mods$model_id, 
                            CI = 95, 
                            order = levels(top_mods$model_id)) +
  scale_color_brewer(name = 'Top Models', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

bad_mods <- model_meta |> 
  filter(!model_id %in% top_mods$model_id) |> 
  pull(model_id)

bad_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = bad_mods, 
                   CI = 80, 
                   order = bad_mods) +
  theme_bw() +
  scale_colour_discrete(name = '') +
  scale_y_continuous(limits = c(0, 100)) + 
  theme(legend.position = 'bottom') + 
  guides(colour = guide_legend(nrow = 5))

bad_95 <- plot_reliability(scores = temperature_scores,
                            models = bad_mods, 
                            CI = 95, 
                            order = bad_mods) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

ggarrange(ggarrange(ggarrange(get_legend(good_80), NULL, nrow = 2),
          ggarrange(good_80, good_95, bad_80, bad_95, align = 'hv', legend= 'none'), ncol = 2, 
          widths = c(1,5)),
          ggarrange(NULL, get_legend(bad_80), ncol = 2, widths = c(1,5)),
          ncol = 1, heights = c(5, 1)) |> 
  ggsave(filename = 'Plots/Figure4.png', height = 17.6, width = 22, units = 'cm')
```

## Figure 5
```{r model_type-site}
n_model_type <- temperature_skill |> 
  distinct(model_id) |> 
  left_join(model_meta) |>
  group_by(model_type) |> 
  summarise(n = n())  |> 
  mutate(site_id = 'TOOK', mean_skill = -3.5) |> 
  filter(model_type != 'null')

@@

A <- temperature_skill |> 
  left_join(model_meta, by = 'model_id') |>
  filter(model_type != 'null') |> 
  group_by(model_type, model_id, site_id) |> 
  summarise(mean_skill = mean(skill_crps, na.rm = T)) |>  
  ggplot(aes(x = mean_skill, 
             y = site_id, 
             colour = model_type)) +
  geom_vline(xintercept = 0, linetype = 'solid') +
  geom_label(data = n_model_type, aes(label = paste0('n = ', n)))+ 
  geom_boxplot() +
  facet_wrap(~model_type, scales = 'free_y',nrow = 4) +
  labs(y='Site', x = 'mean CRPS skill (vs climatology)') +
  scale_colour_manual(values = cols_modeltype) +
  theme_bw()

B <- temperature_skill |> 
  filter(model_id %in% top_mods$model_id) |> 
  group_by(site_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  mutate(site_id = factor(site_id, levels = lake_sites)) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = site_id)) +
  geom_hline(yintercept = 0) + 
  geom_line()  +  
  labs(y='mean CRPS skill (vs climatology)', x = 'Horizon (days)') +
  scale_color_viridis_d(option = 'H') +
  theme_bw()

ggarrange(A, B, widths = c(1,1)) |> 
  ggsave(filename = './Plots/Figure5.png', width = 25, height = 15, units = 'cm')
```

## Figure 6

@@

# is 2023 a stand out year?
obs <- targets |> 
  filter(variable == 'temperature',
         site_id %in% lake_sites, 
         year(datetime) < 2024) |> 
  mutate(doy = yday(datetime),
         year = year(datetime),
         is_2023 = ifelse(year == 2023, 2023, 2022),
         site_id = factor(site_id, levels = lake_sites)) |> 
  ggplot(aes(x=doy, y=observation, colour = is_2023)) +
  geom_jitter(show.legend = F, aes(alpha = is_2023), size = 0.7, height = 0.2) +
  facet_manual(~factor(site_id, levels = lake_sites),
                 design = layout_design) +
  scale_colour_viridis_c(option = 'mako', begin = 0.1, end = 0.8) +
  labs(x= 'Day of year', y = 'Observation (°C)') +
  scale_alpha(range = c(0.5, 0.8))+
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,35)) +
  theme_bw()

cv_obs <- 
  targets |> 
  mutate(site_id = factor(site_id, levels = lake_sites), 
         year = year(datetime)) |> 
  filter(variable == 'temperature',
         site_id %in% lake_sites,
         year < 2024) |> 
  group_by(site_id, year, variable) |> 
  summarise(cv = sd(observation, na.rm = T)/ mean(observation, na.rm = T)) |> 
  mutate(is_2023 = ifelse(year == 2023, '2023', 'other years' )) |> 
  ggplot(aes(y = site_id, x = cv, colour = is_2023)) +
  geom_point() +
  scale_colour_viridis_d(option = 'mako', begin = 0.8, end = 0.1, name = '') +
  scale_y_discrete(limits = rev)+
  theme_bw() +
  labs(x = 'Coefficient of variation', y = 'Site')

ggarrange(obs, cv_obs, widths = c(1, 1.5)) |> 
  ggsave(filename = 'Plots/Figure6.png', width = 20, height=10, units = 'cm')

>>>>

lake_sites <- c('TOOK', 'PRLA','PRPO', 'CRAM', 'LIRO','BARC', 'SUGG')
cols_modeltype <- c('empirical' = "#482576FF",
                    'MME' =  "#35608DFF",
                    'process' = "#21908CFF",
                    'ML' = '#BBDF27FF',
                    'null' = '#A9A9A9')
# read in the metadata from the google sheet
googlesheets4::gs4_deauth()
model_meta <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1oC7_w63wSCXNiHs1IK8AFGr0MG-NdjDAjwkfjvRZW-I/edit?usp=sharing")

@@

```{r model-type, fig.width=10}
top10_temp <- 
  temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |>
  slice_max(mean_crps, n= 10, na_rm = T) |>
  left_join(model_meta) |> 
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'), 
         uses_AT = str_detect(NOAA_var, 'air_temperature')) |> 
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_AT)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", 
                   pattern_spacing = 0.04,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model', x = 'mean relative skill (°C)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw() + 
  guides(pattern = guide_legend(override.aes = list(fill = "white", pattern_spacing = 0.02), 
                                title = 'Uses air temperature as a covariate?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model type'))

all_temp <- 
  temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(model_meta) |> 
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'), 
         uses_AT = str_detect(NOAA_var, 'air_temperature')) |> 
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +    # Different pattern for each group

  geom_bar_pattern(aes(pattern = as.factor(uses_AT)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", width = 0.8,
                   pattern_spacing = 0.03,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model', x = 'mean relative skill (°C)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe'), name = 'Uses air temperature as a covariate?') +
  scale_pattern_type_manual(values=c(NA, NA), name = 'Uses air temperature as a covariate?') +
  theme_bw() + 
  guides(pattern = guide_legend(override.aes = list(fill = "white"), title = 'Uses air temperature as a covariate?'),
         fill = guide_legend(override.aes = list(pattern = "none"), title = 'Model type'))

@@

## Figure 2
```{r skill-bias-sd}
# top 10 average models
top_mods <- temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |> 
  slice_max(mean_crps, n = 10, na_rm = T) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps, .desc = T)) |> 
  distinct(manuscript_name, model_id)

skill <- 
  temperature_skill |> 
  filter(model_id %in% top_mods$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(top_mods$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = manuscript_name)) +
  geom_hline(yintercept = 0, colour = 'grey40' ) + 
  geom_line()  +  
  labs(y='mean relative skill (°C)', x = 'Horizon (days)') +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw()

sd <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime)) |> 
  filter(model_id %in% top_mods$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_sd = mean(sd, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(top_mods$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_sd, colour = manuscript_name)) +
  geom_line()+
  labs(y='mean standard deviation (°C)', x = 'Horizon (days)') +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw()

bias <- temperature_scores |> 
  mutate(horizon = as_date(datetime) - as_date(reference_datetime),
         abs_bias = abs(mean - observation)) |> 
  filter(model_id %in% top_mods$model_id, 
         horizon > 0, 
         horizon != 15,
         horizon <= 30) |>
  group_by(model_id, horizon) |> 
  summarise(mean_abs_bias = mean(abs_bias, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  mutate(manuscript_name = factor(manuscript_name, levels = levels(top_mods$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_abs_bias, colour = manuscript_name)) +
  geom_line()+
  labs(y='mean absolute bias (°C)', x = 'Horizon (days)') +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw() +
  coord_cartesian(ylim = c(0, 2.5))

ggpubr::ggarrange(skill, 
                  ggarrange(as_ggplot(get_legend(bias)), NULL, widths = c(0.5, 1.5)),  
                  sd, 
                  bias, 
                  legend = F, align = 'hv') |> 
  ggsave(filename = 'Plots/Figure2.png', height = 16, width = 16, units = 'cm')
```

## Figure 3

@@

good_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = top_mods, # model_ids and manuscript names
                   CI = 80, 
                   order = levels(top_mods$manuscript_name)) +
  scale_color_brewer(name = 'Top Models', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

good_95 <- plot_reliability(scores = temperature_scores,
                            models = top_mods, 
                            CI = 95, 
                            order = levels(top_mods$manuscript_name)) +
  scale_color_brewer(name = 'Top Models', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

# get the list of bad models
bad_mods <- model_meta |> 
  filter(!model_id %in% top_mods$model_id) |> 
  select(model_id, manuscript_name)

bad_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = bad_mods, 
                   CI = 80, 
                   order = bad_mods$manuscript_name) +
  theme_bw() +
  scale_colour_discrete(name = '') +
  scale_y_continuous(limits = c(0, 100)) + 
  theme(legend.position = 'bottom') + 
  guides(colour = guide_legend(nrow = 5))

bad_95 <- plot_reliability(scores = temperature_scores,
                            models = bad_mods, 
                            CI = 95, 
                            order = bad_mods$manuscript_name) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

ggarrange(ggarrange(ggarrange(get_legend(good_80), NULL, nrow = 2),
          ggarrange(good_80, good_95, bad_80, bad_95, align = 'hv', legend= 'none'), ncol = 2, 
          widths = c(1,5)),
          ggarrange(NULL, get_legend(bad_80), ncol = 2, widths = c(1,5)),
          ncol = 1, heights = c(5, 1)) |> 
  ggsave(filename = 'Plots/Figure3.png', height = 17.6, width = 23, units = 'cm')
```

## Figure 4
```{r model_type-site}
n_model_type <- temperature_skill |> 
  distinct(model_id) |> 
  left_join(model_meta) |>
  group_by(model_type) |> 
  summarise(n = n())  |> 
  mutate(site_id = 'TOOK', mean_skill = -3.25) |> 
  filter(model_type != 'null')

@@

A <- temperature_skill |> 
  left_join(model_meta, by = 'model_id') |>
  filter(model_type != 'null') |> 
  group_by(model_type, model_id, site_id) |> 
  summarise(mean_skill = mean(skill_crps, na.rm = T)) |>  
  ggplot(aes(x = mean_skill, 
             y = site_id, 
             colour = model_type)) +
  geom_vline(xintercept = 0, linetype = 'solid') +
  geom_label(data = n_model_type, aes(label = paste0('n = ', n)))+ 
  geom_boxplot() +
  facet_wrap(~model_type, scales = 'free_y',nrow = 2) +
  labs(y='Site', x = 'mean relative skill (°C)') +
  scale_colour_manual(values = cols_modeltype, name = 'Model Type') +
  theme_bw()

B <- temperature_skill |> 
  filter(model_id %in% top_mods$model_id) |> 
  group_by(site_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  mutate(site_id = factor(site_id, levels = lake_sites)) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = site_id)) +
  geom_hline(yintercept = 0, colour = 'grey40') + 
  geom_line()  +  
  labs(y='mean relative skill (°C)', x = 'Horizon (days)') +
  scale_color_viridis_d(option = 'H', name  = 'Site') +
  theme_bw()

cowplot::plot_grid(A, B, nrow = 2, rel_heights = c(1.5, 1), align = 'v', axis = 'lr', labels = 'auto') |> 
  ggsave(filename = './Plots/Figure4.png', width = 19, height = 16, units = 'cm')
```

## Figure 5

@@

# is 2023 a stand out year?
obs <- targets |> 
  filter(variable == 'temperature',
         site_id %in% lake_sites, 
           year(datetime) < 2024) |> 
  mutate(doy = yday(datetime),
         year = year(datetime),
         is_2023 = ifelse(year == 2023, '2023', 'other years' ),
         site_id = factor(site_id, levels = lake_sites)) |> 
  ggplot(aes(x=doy, y=observation, colour = is_2023)) +
  geom_jitter(aes(alpha = is_2023), size = 0.7, height = 0.2) +
  facet_manual(~factor(site_id, levels = lake_sites),
               design = layout_design) +
  scale_colour_viridis_d(option = 'mako', begin = 0.8, end = 0.1, name ='') +
  labs(x= 'Day of year', y = 'Observation (°C)') +
  scale_alpha_manual(values = c(0.7, 0.5), name = '', guide = F)+
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,35)) +
  theme_bw() + 
  theme(legend.position = c(0.75, 1))

cv_obs <- 
  targets |> 
  mutate(site_id = factor(site_id, levels = lake_sites), 
         year = year(datetime)) |> 
  filter(variable == 'temperature',
         site_id %in% lake_sites,
         year < 2024) |> 
  group_by(site_id, year, variable) |> 
  summarise(cv = sd(observation, na.rm = T)/ mean(observation, na.rm = T)) |> 
  mutate(is_2023 = ifelse(year == 2023, '2023', 'other years' )) |> 
  ggplot(aes(y = site_id, x = cv, colour = is_2023)) +
  geom_point(show.legend = F) +
  scale_colour_viridis_d(option = 'mako', begin = 0.8, end = 0.1, name = '') +
  scale_y_discrete(limits = rev)+
  theme_bw() +
  labs(x = 'Coefficient of variation', y = 'Site')

ggarrange(obs, cv_obs, widths = c(1, 1.5), labels = 'auto') |> 
  ggsave(filename = 'Plots/Figure5.png', width = 20, height=10, units = 'cm')
